Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-12 pecomplexity.tex
added sentence to abstract

\begin{abstract}
{\color{green}From the site: It should be about 5\% of the length of the article, but less than 500 words.}

This paper provides insight into when, why, and how forecast
strategies fail when they are applied to complicated time series.  We
conjecture that the inherent complexity of a time series---which
results from the inherent dimension, nonlinearity, and
non-stationarity of the generating process, as well as from
measurement issues like noise, aggregation, and finite data
length---is both \emph{empirically quantifiable} and \emph{directly
  correlated with predictability}.  To validate this conjecture, we
study 120 different time-series data sets and a wide variety of
forecast models.  We estimate the complexity of each data set using a
variant of permutation entropy, then compare that complexity with the
accuracy of each forecast method.

>>>>

\begin{abstract}

This paper provides insight into when, why, and how forecast
strategies fail when they are applied to complicated time series.  We
conjecture that the inherent complexity of a time series---which
results from the inherent dimension, nonlinearity, and
non-stationarity of the generating process, as well as from
measurement issues like noise, aggregation, and finite data
length---is both \emph{empirically quantifiable} and \emph{directly
  correlated with predictability}.  To validate this conjecture, we
study 120 different time-series data sets and a wide variety of
forecast models.  We estimate the complexity of each data set using a
variant of permutation entropy, then compare that complexity with the
accuracy of each forecast method.  We use the results to develop a
heuristic that can help practitioners recognize when a particular
prediction method is not well matched to the task at hand: that is,
when the time series has more predictive structure than that method
can capture and exploit.
